\documentclass{ruthesis}
\special{papersize=8.5in,11in} % for A4-default configurations on servers


\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{amssymb,amsmath,amsfonts}
\usepackage{amsbsy}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{booktabs}
\usepackage{algorithm2e}
\usepackage{listings}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage{subcaption}
\usepackage{changepage}
\usepackage{soul}
\usepackage{float}

\acrodef{QoS}{Quality of Service}
\acrodef{VM}{Virtual Machine}
\acrodef{UDF}{User Defined Function}
\acrodef{DAG}{Directed Acyclic Graph}
\acrodef{CEP}{Complex Event Processing}
\acrodef{IoT}{Internet of Things}
\acrodef{DSPE}{Data Stream Processing Engine}
\acrodef{DSP}{Data Stream Processing}
\acrodef{FCFS}{First-Come, First-Served}
\acrodef{SPDG}{Series-Parallel-Decomposable Graphs}
\acrodef{IPS}{Instructions per Second}
\acrodef{RTR}{Response Time Rate}
\acrodef{CR+RP}{Cost Rate with Region Patterns}
\acrodef{CI}{Cloud Infrastructure}
\acrodef{EI}{Edge Infrastructure}
\acrodef{LB}{Taneja et. al.}
\acrodef{DSP}{Distributed Stream Processing}
\acrodef{MIPS}{Millions of Instructions per Second}
\acrodef{SDN}{Software Defined Network}
\acrodef{SoC}{System on a Chip}
\acrodef{CDF}{Cumulative distribution function}
\acrodef{OODA}{Observe Orient Decide Act}

% set the default code style
\lstset{
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=1, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    basicstyle=\small,
    keywordstyle=[1]\color{green},
    keywordstyle=[2]\color{orange},
    keywordstyle=[3]\color{blue},
}

\lstdefinelanguage{mylang}{
  alsoletter={*,", 10, >=, :, 74,40,-},
  keywords=[1]{placement, minEndToEndLatency, minDataTransferRate, minMessagingCost},
  keywords=[2]{core, edge, *},
  keywords=[3]{new},
}

\begin{document}
\phd

%\title{Enabling Data-driven Stream Processing Pipelines for Edge Computing}
\title{Programming and Managing Data-Driven Applications between the edge and the cloud}
\author{Eduard Gibert Renart}
\program{Computer Science}
\director{Manish Parashar}
\approvals{4}
\submissionyear{2017}
\submissionmonth{May}

\abstract{Due to the proliferation of the Internet of Things (IoT), the number of devices connected to the Internet is growing. These devices are generating unprecedented amounts of data at the edge of the infrastructure. Although the generated data provides great potential, identifying and processing relevant data points hidden in streams of unimportant data, and doing this in near real time, remains a significant challenge. The prevalent model of moving data from the edge to the cloud of the network is quickly becoming unsustainable. Resulting in  an impact on latency, network congestion, storage cost, and privacy, limiting the potential impact of IoT. These observations can be leveraged to design hybrid architectures that can effectively leverage both the edge and the cloud resources to process the data in an effective and timely manner. Although the cloud is better suited to perform heavier (resource intensive) analysis, such as processing historical events and very large datasets, edge devices can support real-time analytics that consider the temporal and spatial characteristics of IoT data. While edge processing can benefit IoT applications, edge resources are typically constrained in their capabilities. In addition integrating edge computing can also add complexity to applications, especially when they need to include policies that govern what kind of data is processed and analyzed at the edge and what is sent to cloud.

To address these challenges, this dissertation presents an IoT Edge Framework, called R-Pulsar, that extends cloud capabilities to local devices and provides a programming model for deciding what, when, where and how data get collected and processed. This thesis makes the following contributions: (1) A content- and location-based programming abstraction for specifying \textbf{what} data gets collected and \textbf{where} the data gets analyzed. (2) A rule-based programming abstraction for specifying \textbf{when} to trigger data-processing tasks based on data observations. (3) A programming abstraction for specifying \textbf{how} to split a given dataflow and place operators across edge and cloud resources. (4) An operator placement strategy that aims to minimize an aggregate cost which covers the end-to-end latency (time for an event to traverse the entire dataflow), the data transfer rate (amount of data transferred between the edge and the cloud) and the messaging cost (number of messages transferred between edge and the cloud). (5) Performance optimizations on the data-processing pipeline in order to achieve real-time performance on constrained devices.

The applicability of this work to real-world IoT applications is validated through a series of experiments performed using embedded devices (Raspberry Pi and Android phone).}

\beforepreface
\acknowledgements{The body of the acknowledgements}
\dedication{The body of the dedication}
\afterpreface

\listoftables
\listoffigures

\chapter{Introduction}
\input{Introduction.tex}
\chapter{Motivating Applications and Requirements} \label{chap:applications}
\input{Motivation.tex}
\chapter{Background and Related Work}
\input{RelatedWork.tex}
\chapter{Associative Rendezvous (AR)} \label{chap:AR}
\input{Chapter1.tex}
\chapter{Enabling Data-driven IoT Applications}
\input{Chapter2.tex}
\chapter{R-Pulsar, an edge-based middleware}
\input{Chapter3.tex}
\chapter{Application to the Distributed Operator Placement Problem}
\input{Chapter4.tex}
\chapter{Conclusion}
\input{Conclusion.tex}

\bibliographystyle{ieeetr}
\bibliography{References}

%\begin{vita}
%\heading{The author of my thesis} \vspace{15pt}
% Colleges attended, with dates, subjects, degrees
%\begin{descriptionlist}{xxxxx-xxxxx} % reverse chronological order
%\item[200x] Ph. D. in Computer Science, Rutgers University
%\item[200x-0x] B. Sc. in Computer Science from some University
%\item[200x] Graduated from such and such high school.
%\end{descriptionlist}
%\medskip
%\begin{descriptionlist}{xxxxx-xxxxx} %positions held since BS degree
%\item[200x-200y] Teaching assistant, Department of Computer Science, Rutgers University
%\end{descriptionlist}
%\end{vita}

\end{document}
